Irt plot extra

### 2022-03-30 manuscript.Rmd
Person fit 5 axis lebel changed

F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme+ylim(0,600) + xlim(-4,2)

>>>>

F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F5")+apatheme+ylim(0,600) + xlim(-4,2)
